### 2013-06-24 trunk/network-science/paper.tex

\begin{abstract}
We address the dynamic properties of typical social networks. We suppose
the evolution over time only includes new connections between existing or newly
created nodes. We study the activity and centrality
metrics for nodes in such graphs by regulating a series of reasonable
properties the metrics should satisfy. We then formally define our metrics and
give their mathematical analysis. We have developed a practice based framework
to maintain the evolving large-scale network and the algorithm to compute our
metrics including historical queries in preferable time and space consumption.
Finally, we use a simple model to generate evolving data from existing social
network data and compare our metrics to static metrics. The results could imply
that dynamic centrality is more capable in spotting hot social events.

>>>>

\begin{abstract}
This paper addresses the dynamic properties of typical social networks. We
suppose the evolution over time only includes creating new edges but no
deletion. The paper studies the activity and centrality metrics for nodes in
such graphs by regulating a series of reasonable properties the metrics should
satisfy. Then formal definition is given for our metrics and
also their mathematical analysis. We have developed a practice based framework
to maintain the evolving large-scale network and an algorithm to compute our
metrics including historical queries in acceptable time and space consumption.
Finally, we use a simple model to generate evolving graph from existing social
network data and compare our metric to the static one. The results could imply
that dynamic centrality is more capable in spotting hot social events.
